Using Fundamental Measure Theory to treat the two-point pair distribution function of the Inhomogeneous Hard-Sphere Fluid

### 2013-06-21 papers/pair-correlation/paper.tex

\section{What does it look like (graphs that show the function itself)?}
\subsection{Fit to radial distribution function}
%% Figure~\ref{fig:radial-distribution} shows...
%% \begin{figure}
%%   \Huge{Need figure here}
%%   \caption{Plot of the radial distribution function, with our fit.}\label{fig:radial-distribution}
%% \end{figure}
%% \subsection{Pair distribution function}
%% Figure~\ref{fig:pair-distribution} shows...
%% \begin{figure}
%%   \Huge{Need figure here}
%%   \caption{Plot of the pair distribution function near a hard wall.
%%     How do we plot this?}\label{fig:pair-distribution}
%% \end{figure}

%% \section{How well does it work?}
%% Figure~\ref{fig:dadz} shows...
%% \begin{figure}
%%   \includegraphics[width=5cm]{figs/dadz}
%%   \caption{Plot of $\frac{da_1}{dz}$ near a hard
%%     wall. For what $\Phi$?}\label{fig:dadz}
%% \end{figure}

>>>>

\section{What does it look like (graphs that show the function itself)?}
\subsection{Fit to radial distribution function}
Figure~\ref{fig:radial-distribution} shows...
\begin{figure}
  \includegraphics[width=3cm]{figs/ghs-g}
  \includegraphics[width=3cm]{figs/ghs-g-ghs}
  \caption{Plot of the radial distribution function, with our fit.}\label{fig:radial-distribution}
\end{figure}
\subsection{Pair distribution function}
Figure~\ref{fig:pair-distribution} shows...
\begin{figure}
  \includegraphics[width=6cm]{figs/pair-correlation-2-395-5}
  \caption{Plot of the pair distribution function near a hard wall.
    How do we plot this?}\label{fig:pair-distribution}
\end{figure}

\section{How well does it work?}
Figure~\ref{fig:dadz} shows...
\begin{figure}
  \includegraphics[width=3cm]{figs/dadz-3-2}
  \includegraphics[width=3cm]{figs/dadz-3-3}
  %%\includegraphics[width=3cm]{figs/dadz-4-3}
  \caption{Plot of $\frac{da_1}{dz}$ near a hard
    wall. For what $\Phi$?}\label{fig:dadz}
\end{figure}
